<<<<<<< HEAD
\section{Introduccion}

La tarea Hack2026 se formula como retrieval visual multietiqueta: dada una imagen de bundle, el sistema debe recuperar los \texttt{product\_asset\_id} correctos y ordenar hasta 15 candidatos por bundle para evaluacion.

La base actual del repositorio es OpenCLIP (Marqo Fashion SigLIP) con varias rutas de inferencia especializadas. A nivel de ingenieria, el flujo de trabajo se divide en:
\begin{enumerate}
  \item Preparacion de datos e imagenes (\texttt{download.sh}, \texttt{preprocess\_data.py}, \texttt{offline\_augment.py}).
  \item Entrenamiento de retrieval multimodal (\texttt{python -m src.train}, backend \texttt{src/models/retrieval\_openclip.py}).
  \item Inferencia y exportacion de submission (\texttt{src.infer}, \texttt{src.new\_infer}, \texttt{src.infer\_phase1}, \texttt{src.infer\_top1}, \texttt{src.infer\_openclip}).
\end{enumerate}

Adicionalmente, el proyecto incluye scripts de analisis para explotar senales de metadata temporal y estructura categoria-seccion (por ejemplo, \texttt{src/utils/check\_link\_timestamps.py}).

Este documento resume la implementacion vigente y los artefactos observables del workspace.
=======
\section{Introduction}

The Hack2026 task is a multi-label visual retrieval problem: given a bundle image (an outfit or set of garments), the system must predict the list of product identifiers (\texttt{product\_asset\_id}) present in that bundle. The final output is a CSV with one row per predicted product, grouped by \texttt{bundle\_asset\_id}, with a maximum of 15 predictions per bundle.

This repository implements two complementary approaches:
\begin{enumerate}
  \item A lightweight pretrained baseline (\texttt{src/infer.py}) based on cosine retrieval over image embeddings from torchvision backbones.
  \item A trainable multimodal retrieval model (\texttt{src/models/retrieval\_openclip.py}) based on Marqo Fashion SigLIP, with optional bundle-region detection and contrastive optimization.
\end{enumerate}

From an engineering perspective, the codebase is organized around three stages:
\begin{enumerate}
  \item Data curation and asset preparation (\texttt{preprocess\_data.py}, \texttt{download.sh}, \texttt{offline\_augment.py}).
  \item Training and local validation (\texttt{src/train.py} with Hydra config).
  \item Test-time inference and submission export (\texttt{src/infer.py}, \texttt{src/infer\_openclip.py}).
\end{enumerate}

This paper documents the end-to-end pipeline and the practical decisions embedded in the current implementation.
>>>>>>> e9d5d43845f1bcb17b1a4f5c33b124b3b6907bf4
