<<<<<<< HEAD
\section{Protocolo Experimental}

\subsection{Estrategia de Evaluacion Local}

La evaluacion local se ejecuta en inferencia con split por \texttt{bundle\_asset\_id} controlado por \texttt{infer.val\_ratio}. Segun entrypoint, se reportan \texttt{Hit@K}/\texttt{Recall@K} para \texttt{infer.eval\_ks}:
\begin{enumerate}
  \item \texttt{src.infer} (pipeline principal).
  \item \texttt{src.new\_infer} (v8).
  \item \texttt{src.infer\_phase1}.
  \item \texttt{src.infer\_top1}.
\end{enumerate}

\subsection{Artefactos de Salida}

Artefactos frecuentes del flujo train/infer:
\begin{itemize}
  \item \texttt{metrics.jsonl}, \texttt{best.pt}, \texttt{epoch\_X.pt} en entrenamiento.
  \item \texttt{test\_submission.csv} y \texttt{val\_metrics.json} para \texttt{src.infer}.
  \item \texttt{test\_submission\_v8.csv}, \texttt{val\_metrics\_v8.json} para \texttt{src.new\_infer}.
  \item \texttt{test\_submission\_phase1.csv}, \texttt{val\_metrics\_phase1.json} para \texttt{src.infer\_phase1}.
  \item \texttt{test\_submission\_top1.csv}, \texttt{val\_metrics\_top1.json} para \texttt{src.infer\_top1}.
\end{itemize}

\subsection{Reportes Analiticos Observados en el Workspace}

\texttt{outputs/ts\_date\_alignment\_report.csv} (1,876 bundles):
\begin{itemize}
  \item 6,493 productos enlazados con timestamp disponible.
  \item 12.26\% de productos comparten fecha exacta bundle-producto.
  \item 54.57\% comparten mes.
  \item 81.01\% comparten trimestre.
\end{itemize}

\texttt{outputs/category\_section\_summary.json}:
\begin{itemize}
  \item 88 categorias totales en joins train.
  \item Para categorias con al menos 30 muestras: 9 son single-section y 10 casi single-section (umbral de pureza 0.95).
=======
\section{Experimental Protocol}

\subsection{Local Evaluation Strategy}

The repository provides two local validation pathways:
\begin{enumerate}
  \item Baseline mode (\texttt{src/infer.py}) samples validation bundles with \texttt{infer.val\_ratio} and reports \texttt{hit@K}/\texttt{recall@K}.
  \item Training mode (\texttt{src/models/retrieval\_openclip.py}) evaluates \texttt{recall@K} after each epoch, where $K=\texttt{params.recall\_k}$.
\end{enumerate}

Products are indexed once per validation pass, bundles are encoded, and top-K nearest neighbors are retrieved by cosine similarity.

\subsection{Output Artifacts}

Main artifacts generated by the training/inference workflow:
\begin{itemize}
  \item \texttt{metrics.jsonl}: epoch-level train loss and validation recall.
  \item \texttt{best.pt}: best checkpoint by recall metric.
  \item \texttt{test\_submission.csv}: final prediction file for competition upload.
  \item \texttt{val\_metrics.json}: baseline run summary and local metrics.
\end{itemize}

\subsection{Recommended Ablations}

To measure impact of major components, the following ablations are recommended:
\begin{itemize}
  \item Image-only products vs. image+text product embeddings.
  \item Bundle full-image encoding vs. detection-guided region aggregation.
  \item No offline augmentation vs. deterministic offline augmentation.
  \item Single-GPU vs. multi-GPU, with fixed seed and equal effective batch size.
>>>>>>> e9d5d43845f1bcb17b1a4f5c33b124b3b6907bf4
\end{itemize}
